---
title: "p8105_hw5_wb2366"
auther: Wenhan Bao
Date: 2021-11-18
output: github_document
---

```{r}
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem2

**Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time**

```{r}
study_df_header <- list.files(path = "./data-2", pattern = "csv") %>% 
  as.data.frame() %>% 
  rename(subject_id = 1)

study_df_data <- list.files(path = "./data-2", pattern = "csv", full.names = T) %>% 
  map_df(read.csv) %>% 
  cbind(study_df_header,.) %>% 
  mutate(subject_id = str_sub(subject_id, end = 6)) %>% 
  separate(col = subject_id, into = c("arm", "subject_id")) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "score")
```

**Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.**

```{r}
study_df_data %>%
  mutate(arm = case_when(arm == "con" ~ "Control",
                         arm == "exp" ~ "Experiment")) %>%
  ggplot(aes(
    x = week,
    y = score,
    color = arm,
    group = interaction(arm, subject_id)
  )) +
  geom_line() +
  labs(title = "Data observated on each subject over time for two arms",
       x = "Week",
       y = "Data for the longitudinal study") +
  scale_x_discrete(labels = c(
    "Week 1",
    "Week 2",
    "Week 3",
    "Week 4",
    "Week 5",
    "Week 6",
    "Week 7",
    "Week 8"
  )) +
  theme(plot.title = element_text(hjust = 0.5)) +
  viridis::scale_color_viridis(discrete = TRUE)
```

**Answer:** According to the "spaghetti" plot, when concentrating on the difference between two groups, we are easy to figure out that the mean data value for experiment arm is obviously larger than the mean data value for control arm.

## Problem3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

**Write a function that takes a vector as an argument**

```{r}
fill_missing = function(x){
  
  if(is.numeric(x)){
    x = replace(x, is.na(x), mean(x, na.rm = T))
  }
  else if(is.character(x)){
    x = replace(x, is.na(x), "virginica")
  }
  
  x
}
```

**replaces missing values using the rules defined above**

```{r}
iris_df = map_df(.x = iris_with_missing, ~ fill_missing(.x))
```



